---
title: dat_all_final
output: html_notebook
---
 
 
### Abstract
TBA
 
 
### Setup
 
```{r setup}
suppressWarnings(suppressMessages({
  library(knitr)
  library(kableExtra)
  library(htmltools)
  library(tidyverse)
  library(scales)
  library(ExPanDaR)
}))
knitr::opts_chunk$set(fig.align = 'center')
```
 
 
### Create Sample
 
This step reads the raw data provided by `ExPanD()` and generates the sample for the analysis.
 
```{r create_sample}
create_sample <- function(df, df_def) {
  # Set infinite numerical variables to NA
  df[, df_def$var_name[df_def$type == "numeric"]] <-
    lapply(df[, df_def$var_name[df_def$type == "numeric"]],
      function(x) ifelse(is.finite(x), x, NA))
 
  # Delete numerical variables that only contain NAs
  all_na_vars <- sapply(df, function (x) all(is.na(x)))
  df_def <- df_def[!all_na_vars,]
  df <- df[, df_def$var_name]
 
  # Drop observations that are NA in variables that are not allowed to
  df <- df[complete.cases(df[, df_def$var_name[which(df_def$can_be_na == FALSE)]]), ]
 
  df <- droplevels(df)
  return(list(df = df, df_def = df_def))
}
 
load("ExPanD_nb_data.Rdata")
 
smp_list <- create_sample(nb_df, nb_df_def)
smp <- smp_list$df
smp_def <- smp_list$df_def
```
 
 
### Bar Chart
 
```{r bar_chart}
df <- smp
df$year <- as.factor(df$year)
df$hi1990 <- as.factor(df$hi1990)
p <- ggplot(df, aes(x = year)) +
  geom_bar(aes(fill = hi1990), position = "fill") +
  labs(x = "year", fill = "hi1990", y = "Percent") +
scale_y_continuous(labels = percent_format())
p <- p + scale_x_discrete(breaks = pretty(as.numeric(as.character(df$year)), n = 10))
p
```
 
 
### Missing Values
 
```{r missing_values}
df <- smp
prepare_missing_values_graph(df, "year")
```
 
 
### Descriptive Statistics
 
```{r descriptive_statistics}
df <- smp
t <- prepare_descriptive_table(smp)
t$kable_ret  %>%
  kable_styling("condensed", full_width = F, position = "center")
```
 
 
### Histogram
 
```{r histogram}
var <- as.numeric(smp$log_lp[smp$year == "1990"])
hist(var, main="", xlab = "log_lp", col="red", right = FALSE, breaks= 25)
```
 
 
### Extreme Observations
 
```{r extreme_obs}
df <- smp
vars <- c("country", "year", "GDPpc", "year")
df <- df[df$year == "1990", ]
df <- df[, vars]
df <- droplevels(df[complete.cases(df), ])
if (nrow(df) <= 10) {
  cat("Not enough data to generate table")
} else {
  tab <- prepare_ext_obs_table(df, var = "GDPpc")
  tab$kable_ret %>%
    kable_styling()
}
```
 
 
### By Group Bar Graph
 
```{r by_group_bar_graph}
df <- smp
df <- df[df$year == "1990", ]
prepare_by_group_bar_graph(df, "hi1990", "lp", mean, TRUE)$plot +
  ylab("mean lp")
```
 
 
### By Group Violin Graph
 
```{r by_group_violin_graph}
df <- smp
prepare_by_group_violin_graph(df, "region", "log_lp", TRUE)
```
 
 
### Trend Graph
 
```{r trend_graph}
df <- smp
prepare_trend_graph(df, "year", c("lp"))$plot
```
 
 
### Quantile Trend Graph
 
```{r quantile_trend_graph}
df <- smp
prepare_quantile_trend_graph(df, "year", c(0.05, 0.25, 0.5, 0.75, 0.95), "lp")$plot
```
 
 
#### lp  
```{r}
log_lp_raw <- prepare_quantile_trend_graph(smp, "year", c(0.05, 0.25, 0.5, 0.75, 0.95), "log_lp_raw")$plot
```


```{r}
log_lp_raw <- log_lp_raw +
theme_minimal() +
  guides(color = guide_legend(reverse = TRUE)) +
  scale_color_discrete(name = "Quantile") +
  labs(x = "",
       y = "Log of Labor Productivity")
ggsave("quintiles_all_log_lp_raw.pdf", width = 6, height = 4)
```

```{r}
Qre_log_lp_World <- prepare_quantile_trend_graph(smp, "year", c(0.05, 0.25, 0.5, 0.75, 0.95), "re_log_lp")$plot
```


```{r}
Qre_log_lp_World +
theme_minimal() +
  guides(color = guide_legend(reverse = TRUE)) +
  scale_color_discrete(name = "Quantile") +
  labs(x = "",
       y = "Relative (log) labor productivity")
ggsave("Qre_log_lp_World.pdf", width = 6, height = 4)
```




#### ky  

```{r}
log_ky_raw <- prepare_quantile_trend_graph(smp, "year", c(0.05, 0.25, 0.5, 0.75, 0.95), "log_ky_raw")$plot
```


```{r}
log_ky_raw <- log_ky_raw +
theme_minimal() +
  guides(color = guide_legend(reverse = TRUE)) +
  scale_color_discrete(name = "Quantile") +
  labs(x = "",
       y = "Log of Capital-Output Ratio")
ggsave("quintiles_all_log_ky_raw.pdf", width = 6, height = 4)
```   


#### h  

```{r}
log_h_raw <- prepare_quantile_trend_graph(smp, "year", c(0.05, 0.25, 0.5, 0.75, 0.95), "log_h_raw")$plot
```


```{r}
log_h_raw <- log_h_raw +
theme_minimal() +
  guides(color = guide_legend(reverse = TRUE)) +
  scale_color_discrete(name = "Quantile") +
  labs(x = "",
       y = "Log of Human Capital")
ggsave("quintiles_all_log_h_raw.pdf", width = 6, height = 4)
```  


#### TFP  

```{r}
log_tfp_raw <- prepare_quantile_trend_graph(smp, "year", c(0.05, 0.25, 0.5, 0.75, 0.95), "log_tfp_raw")$plot
```


```{r}
log_tfp_raw <- log_tfp_raw +
theme_minimal() +
  guides(color = guide_legend(reverse = TRUE)) +
  scale_color_discrete(name = "Quantile") +
  labs(x = "",
       y = "Log of Aggregate Efficiency")
ggsave("quintiles_all_log_tfp_raw.pdf", width = 6, height = 4)
```   

 
### Correlation Graph
 
```{r corrplot}
df <- smp
ret <- prepare_correlation_graph(df[, c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 29, 30, 31, 34, 35, 36, 37, 38, 39, 40)])
```
 
 
### Scatter Plot
 
```{r scatter_plot}
df <- smp
df <- df[, c("country", "year", "log_lp", "log_GDPpc", "region", "pop")]
df <- df[complete.cases(df), ]
df$region <- as.factor(df$region)
set.seed(42)
df <- sample_n(df, 1000)
prepare_scatter_plot(df, "log_lp", "log_GDPpc", color = "region", size = "pop", loess = 1)
```
 
 
### Regresssion Table
 
```{r regression}
df <- smp
df <- df[, c("log_lp", "log_ky", "log_h", "log_tfp", "country", "year", "hi1990")]
df <- df[complete.cases(df), ]
df$hi1990 <- as.factor(df$hi1990)
df <- droplevels(df)
t <- prepare_regression_table(df, dvs = "log_lp", idvs = c("log_ky", "log_h", "log_tfp"), feffects = c("country", "year"), clusters = c("country", "year"), byvar = "hi1990", models = "ols")
HTML(t$table)
```
 
 
### Note
 
This Notebook has been automatically generated using the [ExPanDaR](https://joachim-gassen.github.io/ExPanDaR) package.
 
